Longer term All-Cause and Cardiovascular Mortality with Intensive Blood Pressure Control

### 2021-12-23 doc/manuscript.Rmd
multi-panel landscape setup

Nicholas M. Pajewski, PhD^1^ 
Byron C. Jaeger, PhD^1^ 
Paul E. Drawz, DEGREES^2^ 
Paul K. Whelton, DEGREES^3^ 
Mark A. Supiano, DEGREES^4^ 
Jeff D. Williamson, DEGREES^5^, and 
David M. Reboussin, DEGREES^1^

@@

^5^Section on Gerontology and Geriatric Medicine, Wake Forest School of Medicine, Winston-Salem, NC.

@@

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      dpi = 600, 
                      fig.height = 7, 
                      fig.width = 6.75)

@@

tar_load(names = c(recoders,
                   base_viz_inc,
                   base_ds, 
                   long_ds,
                   long_inf,
                   base_inf,
                   ndi_baseline))

base_ds <- mutate(base_ds,
                  variable = str_remove(variable, '^base_ds_'))

long_ds <- mutate(long_ds,
                  variable = str_remove(variable, '^long_ds_'))

long_inf <- mutate(long_inf,
                   variable = str_remove(variable, '^long_inf_'))

base_inf <- mutate(base_inf,
                   variable = str_remove(variable, '^base_inf_'))

@@

\newpage
__Figure 1__: Cumulative incidence of all-cause mortality.

@@

base_viz_inc$acm[[1]]

@@

\newpage
__Figure 2__: Cumulative incidence of cardiovascular and non-cardiovascular mortality.

@@

base_viz_inc$cvd[[1]]

@@

\newpage
# SUPPLEMENT

We have a total of `r nrow(base_viz_inc)`) plots showing all-cause mortality and mortality split into cardiovascular and non-cardiovascular causes. They are automated enough to dynamically set text and axis values that will look reasonable. To show what I mean, I've added the figures for adults 75 years or older, who have a much higher incidence.

@@

base_viz_inc$acm[[3]]

@@

base_viz_inc$cvd[[3]]

@@

>>>>

Byron C. Jaeger, PhD^1^ 
Paul E. Drawz, DEGREES^2^ 
Paul K. Whelton, DEGREES^3^ 
Mark A. Supiano, DEGREES^4^ 
Adam P. Bress, PharmD, MS^5,6^
Jeff D. Williamson, DEGREES^7^
David M. Reboussin, DEGREES^1^, and
Nicholas M. Pajewski, PhD^1^

<!-- Jackson T. Wright Jr., MD, PhD, Alfred K. Cheung, MD, William C. Cushman, MD, Cora E. Lewis, MD, Suzanne Oparil, MD, Michael V. Rocco, MD and Karen Johnson, MD -->

@@

^5^	Informatics, Decision-Enhancement, and Analytic Sciences (IDEAS) Center, Veterans Affairs, Salt Lake City Health Care System, Salt Lake City, UT

^6^	Department of Population Health Sciences, University of Utah School of Medicine, Salt Lake City, UT

^7^Section on Gerontology and Geriatric Medicine, Wake Forest School of Medicine, Winston-Salem, NC.

@@

knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      dpi = 600, 
                      fig.width = 11, 
                      fig.height = 6.25)

@@

tar_load(names = c(recoders,
                   base_viz_inc,
                   base_viz_eff,
                   long_viz_forest,
                   base_ds, 
                   long_ds,
                   long_inf,
                   base_inf,
                   ndi_baseline))

fig <- left_join(base_viz_inc, base_viz_eff)

@@

@@

block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous"
  )
)

@@

__Figure 1__: (A) Cumulative incidence of all-cause mortality by treatment group. (B) Time-dependent effect of being randomized to intensive treatment on all-cause mortality.

@@

blank_plot <- ggplot(data.frame()) + aes() + theme_void()

legend <- get_legend(
  fig$inc_acm[[1]]$plot + 
    theme(legend.position = c(.55, .2),
          legend.direction = 'horizontal')
)

plot_grid(
  # row 1 (legend)
  legend, 
  blank_plot,
  # row 2 (figures)
  fig$inc_acm[[1]]$plot + theme(legend.position = ''), 
  fig$eff_acm[[1]],
  # row 3 (table)
  fig$inc_acm[[1]]$table, 
  blank_plot,
  ncol = 2,
  align = 'v',
  axis = 'lr',
  rel_heights = c(1,10,2),
  labels = c("","","A","B","",""),
  label_x = 0.1,
  label_y = 1.05
)

@@

\newpage
__Figure 2__: (A) Cumulative incidence of cardiovascular and non-cardiovascular mortality by treatment group. (B) Time-dependent effect of being randomized to intensive treatment on cardiovascular mortality.

plot_grid(
  # row 1 (legend)
  legend, 
  blank_plot,
  # row 2 (figures)
  fig$inc_cvd[[1]] + theme(legend.position = ''), 
  fig$eff_cvd[[1]],
  ncol = 2,
  align = 'v',
  axis = 'lr',
  rel_heights = c(1,10,2),
  labels = c("","","A","B","",""),
  label_x = 0.1,
  label_y = 1.05
)

\newpage
__Figure 3__: Hazard ratio for all-cause mortality for participants randomized to intensive versus standard treatment, overall and in subgroups.

long_viz_forest

# SUPPLEMENT

We have a total of `r nrow(base_viz_inc)` plots showing all-cause mortality and mortality split into cardiovascular and non-cardiovascular causes. They are automated enough to dynamically set text and axis values that will look reasonable. To show what I mean, I've added the figures for adults 75 years or older, who have a much higher incidence.

@@

# base_viz_inc$acm[[3]]

@@

# base_viz_inc$cvd[[3]]

@@

```{r}
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    page_margins = page_mar(bottom = 1/8, top = 1/8, 
                            right = 1/4, left = 1/4),
    type = "continuous"
  )
)
```
